Scaffolder - Software for \change{Reproducible}{Manual} Genome Scaffolding.

### 2011-08-15 src/article.tex
Add sentence to discussion

\add{An example use case for Scaffolder is a combination of computational and
manual editing of a genome scaffold. We have used Scaffolder in our own genome
projects to create an initial scaffold from compuationally parsing the output
of \emph{in silico} scaffolding tools into YAML. This scaffold was then
manually updated as the scaffold was finished with additional gap-filling
sequences generated in the laboratory.} \pb

>>>>

\add{A use case for Scaffolder is a combination of computational and manual
editing of a genome scaffold. We have used Scaffolder in our own genome
projects to create an initial scaffold from compuationally parsing the output
of \emph{in silico} scaffolding tools into YAML. This scaffold was then
manually updated as the scaffold was finished with additional gap-filling
sequences generated in the laboratory. This is example of the scaffolder
format being both compuationally tractable while being simple to edit
manually.} \pb
